Fundamentals of Computing and Data Display

### 2019-12-06 Paper/paper-draft-Padgett-Thiam.Rmd
run paper draft

```{r, include = FALSE}
library(knitr)
library(tidyverse)
library(gtrendsR)
library(dplyr)
library(ggplot2)
library(ggmap)
library(readxl)
library(shiny)
library(rtweet)
library(tidytext)
library(stringr)
library(lubridate)
library(quanteda)
library(SentimentAnalysis)
library(GGally)
```

@@

```{r}
polling_data <- read_excel("G:/UMD/JPSM/Fall 2019/SURV727/Project/project polling data.xlsx", sheet=1)
```

@@

```{r, include=FALSE}
#USE THIS CHUNK TO BRING IN props_tab1 and props_tab2
load("G:/UMD/JPSM/Fall 2019/SURV727/Project/props_tab1.RData")
load("G:/UMD/JPSM/Fall 2019/SURV727/Project/props_tab2.RData")

@@

To explore the Google Trends data, we examined the location and density of searches for each candidate. We created a map showing our results. Because it was difficult to see the results for each candidate, we created a shiny app that allows users to toggle between candidates.
```{r, include=FALSE}
#USE THIS CHUNK TO BRING IN gc_locations
load("G:/UMD/JPSM/Fall 2019/SURV727/Project/gc_locations.RData")
```

@@

We also explored the number of hits pre- and post- debate for each candidate.
```{r, include=FALSE}
#USE THIS CHUNK TO BRING IN interest_over_time_all
load("G:/UMD/JPSM/Fall 2019/SURV727/Project/interest_over_time_all.RData")
```

@@

```{r, include=FALSE}
#USE THIS CHUNK TO BRING IN pre_sent_pos and post_sent_pos
load("G:/UMD/JPSM/Fall 2019/SURV727/Project/pre_sent_pos.RData")
load("G:/UMD/JPSM/Fall 2019/SURV727/Project/post_sent_pos.RData")
```

>>>>

```{r, include = FALSE}
library(knitr)
library(tidyverse)
library(gtrendsR)
library(dplyr)
library(ggplot2)
library(ggmap)
library(readxl)
library(shiny)
library(rtweet)
library(tidytext)
library(stringr)
library(lubridate)
library(quanteda)
library(SentimentAnalysis)
library(GGally)
library(repmis)
library(httr)
```

@@

```{r}
github_link <- "https://github.com/znpadgett/surv727_padgett_thiam/raw/master/Data/Project%20polling%20data.xlsx"
temp_file <- tempfile(fileext = ".xlsx")
req <- GET(github_link, 
           write_disk(path = temp_file))
polling_data <- readxl::read_excel(temp_file)
```

@@

```{r, include=FALSE}
#USE THIS CHUNK TO BRING IN props_tab1 and props_tab2
source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab1.RData?raw=true")
source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab2.RData?raw=true")

@@

To explore the Google Trends data, we examined the location and density of searches for each candidate. We created a map showing our results. Because it was difficult to see the results for each candidate, we created a shiny app that allows users to toggle between candidates.
```{r, include=FALSE}
#USE THIS CHUNK TO BRING IN gc_locations
source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/gc_locations.RData?raw=true")
```

@@

We also explored the number of hits pre- and post- debate for each candidate.
```{r, include=FALSE}
#USE THIS CHUNK TO BRING IN interest_over_time_all
source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/interest_over_time_all.RData?raw=true")
```

@@

```{r, include=FALSE}
#USE THIS CHUNK TO BRING IN pre_sent_pos and post_sent_pos
source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/post_sent_pos.RData?raw=true")
source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/pre_sent_pos.RData?raw=true")
```
